---
title: Basics of R
date: 2022-01-02
menu:
  sidebar:
    name: Basics of R
    identifier: Basics of R
    parent: R
    weight: 30
tags: ["Series", "R"]
categories: ["Series-R"]
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

<span class="firstcharacter">T</span>his is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



<style>
body {
text-align: justify
}
</style>

<style>
.firstcharacter {
  color: #903;
  float: left;
  font-family: Georgia;
  font-size: 75px;
  line-height: 60px;
  padding-top: 4px;
  padding-right: 8px;
  padding-left: 3px;
}
</style>

<style>
.comment {
  color: #999999;
  float: left;
  font-size: 12px;
  font-style: italic;
}
</style>
